City traffic, IoT and Blockchain technologies

### 2020-10-25 thesis/report2.tex
Some report 2 paragraphs about security in blockchains.

    \paragraph{Security} Security in Ethereum is a complex process. If an account, being a user's account or a contract account, has successfully secured the private signing key, it is assured that no one can simulate it and no one can execute transactions on its behalf. Known breaches have always occured in the same way: private keys have been leaked and malicious actors were able to execute transactions with them.
    An approach in securing IoT networks is described in \cite{SecureCommunicatingThingsNetworkFramework}. The aim is to ensure secure product shipment, as well as connecting manufacturing locations from different geographical locations. They have a front end for human interactions and a back end for the internal communication of the blockchain network. In the blockchain networks there are two types of associates, the authentication nodes also known is miners and execution nodes. The authentication nodes take care of validating new transactions and keeping up to date with the ever growing blockchain in which they participate. The executing nodes are watching accumulating values and verify their validity. The authors are considering various scenarios like traceability of product records, illegal activities made by workers or shippments. Transactions like those are always embedding the previous block's hash, providing a secure way around manipulating

>>>>

    \paragraph{Security} Security in Ethereum is a complex process. If an account, being a user's account or a contract account, has successfully secured the private signing key, it is assured that no one can simulate it and no one can execute transactions on its behalf. Known breaches have always occured in the same way: private keys have been leaked and malicious actors were able to execute transactions with them.

    An approach in securing IoT networks is described in \cite{SecureCommunicatingThingsNetworkFramework}. The aim is to ensure secure product shipment, as well as connecting manufacturing locations from different geographical locations. They have a front end for human interactions and a back end for the internal communication of the blockchain network. In the blockchain networks there are two types of associates, the authentication nodes also known as miners and execution nodes. The authentication nodes take care of validating new transactions and keeping up to date with the ever growing blockchain in which they participate. The executing nodes are watching accumulating values and verify their validity. The authors are considering various scenarios like traceability of product records, illegal activities made by workers or shippments. Transactions like those are always embedding the previous block's hash, providing a secure way around manipulating or tampering records of shipped items, for example.

    Another proposal of security can be found in \cite{SecuringUserIdentity}. The authors address a more basic need of having IoT devices participating in a M2M (machine-to-machine) network, for extended periods of time. Extended periods of time implies that certificates must be rotated and the old ones shouldn't be exploitable by malicious actors if they are able to compromise those private keys (certificates, in this case, are made of public and private keys pairs where the private key is used by an entity to prove its identity and various details which are part of its identity). Another part of their proposal is to replace raw and uncertified public keys from Bitcoin or Ethereum transcations with Enrollment certificates and transaction certificates. The latter are included in usual transactions while the former are for proving the attributes like identities, identifiers, etc. Transcations certificates are used to hide sensitive information in the public blocks while at the same time to prove the ownership of the entity which made them. To sum up, in author's word, the proposal is a permissioned blockchain technology with \say{privacy-preserving,  traffic-analysis-  resistant methodology  that  leverages  external  trust  relationships  so  as to establish an auditable identity- and attributes- management authorization  framework}.
